Macro Impacts

### 2016-07-14 Macro Impacts Revised.tex
Small clarification.

It is then obvious that $b=0$ corresponds to straight lines. The importance of this observation is that $b^2\approx 10^{-7}\te{s}^{-1}$ and $a^2\approx 10\te{km s}^{-1}$, so the radius of the Poincare sphere corresponding to the trajectories of $p$-waves in earth is approximately $7\times10^3-1\times 10^4\te{km}$, while the earth is of radius $10^3\te{km}$. In particular, for the different layers of the earth, the radius of the layer's outer boundary and its corresponding Poincare sphere is 7.0 for the inner core, 2.0 for the outer core, and 1.8 for the mantle. Thus, it is reasonable to approximate the trajectories of $P$-waves in the inner core as straight lines, but necessary to treat those in the other layers as bending.

>>>>

It is then obvious that $b=0$ corresponds to straight lines. The importance of this observation is that $b^2\approx 10^{-7}\te{s}^{-1}$ and $a^2\approx 10\te{km s}^{-1}$, so the radius of the Poincare sphere corresponding to the trajectories of $p$-waves in earth is approximately $7\times10^3-1\times 10^4\te{km}$, while the earth is of radius $10^3\te{km}$. In particular, for the different layers of the earth, the ratio radius of the layer's outer boundary and the radius of its corresponding Poincare sphere is 7.0 for the inner core, 2.0 for the outer core, and 1.8 for the mantle. Thus, it is reasonable to approximate the trajectories of $P$-waves in the inner core as straight lines, but necessary to treat those in the other layers as bending.
